Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Validation

### 2012-12-28 paper.tex
more numerical stuff

boundary conditions

>>>>

We note a few additional differences between the original PPM
implementation of \citet{ppm} and Castro.  In the original
implementation, the gravitational source term was included in the
characteristic projection.  Here, we follow \citet{ppmunsplit} and add
it afterwards.  In our experiments, projecting the source term did not
make a noticable difference in the energy conservation of the
solution.  Finally, the PPM paper uses an edge-centered gravitational
acceleration in the prediction, whereas we use a cell-centered one.
Both are second-order accurate.  In the unsplit implementation, there
is an additional freedom that comes into play---do we add the source
terms to the normal predictor before or after using it to construct
the transverse flux differences?  Our experiments showed no
substantial difference with either variant.  We add the sources only
at the final construction of the interface states.

The boundary conditions on the hyperbolic system are simply
zero-gradient.  Using AMR, we make the coarse grid very large, so as
to place the boundaries far from the region of interest.  For the
gravity solve, we would like isolated boundary conditions.  Here we
experiment with using two monopoles (one for each star).  The
individual potentials are summed and this is evaluated on the physical
boundary to set Dirichlet conditions for the Poisson solve.
